Smart Model Elimination for Efficient Automated Machine Learning

### 2024-06-21 paper/paper.tex
some updates
final results

\author{%
  Eric Su Zhang\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  St. Mark's School of Texas\\
  10600 Preston Rd, Dallas, TX 75230\\
  \texttt{ericspring08@gmail.com} \\
  % examples of more authors
  \And
  Benjamin Standefer \\
  St. Mark's School of Texas \\
  10600 Preston Rd, Dallas, TX 75230 \\
  \texttt{bjmstandefer@gmail.com} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

\begin{abstract}
  Automated Machine Learning or AutoML has emerged as a popular field of research. We performed a literature review of existing AutoML papers and conducted a survey on six popluar AutoML frameworks. Many of these frameworks optimize a form of model selection, however, they all require most models to be run and evaluated. We propose a novel framework that automatically eliminates models that are unlikely to be performant by training a Boosting Model on hundreds of kaggle datasets. Our framework, SME, demonstrates the ability to generate a model with near equal accuracy to a "dumb" model that runs every model on every dataset, but in a fraction of the time.
\end{abstract}

@@

\begin {figure}
\centering
\fbox{\includegraphics[width=\textwidth]{smeml-flowchart.png}}
\caption{SMEML Process}
\end{figure}

\section{Experiments}
\subsection{Experiment Design}
To evaluate our framework, we choose 7 different datasets of diverse size. We ran SMEML on each dataset for 20 iterations of tuning. We compared this against a "dumb" mode which simply runs every model on the dataset. We used the accuracy and time to train as our metrics.

@@

\subsection{Results}
\begin{table}
  \caption{Experiment Results}
  \label{model-options-table}
  \centering
  \begin{tabular}{llllll}
    \toprule
    % group 2, 3 as multicolumn and 4, 5 as multicolumn
    Dataset & \multicolumn{2}{c}{Accuracy} & \multicolumn{2}{c}{Time to Train (sec)} & Size (RxC)\\
    \cmidrule(lr){2-3} \cmidrule(lr){4-5}
    & SMEML & Dumb & SMEML & Dumb \\
    \midrule
    Chronic Kidney Disease Dataset & 1.0 & 1.0 & 419.64 & 788.46 & 400x26\\
    Brain Stroke Prediction Dataset & .9458 & .9458 & 114.16 & 370.95 & 4892x11\\
    Lung Cancer Prediction & .9839 & .9839 & 143.07 & 317.04 & 309x16\\
    Pima Indians Diabetes Dataset & .7857 & .8052 & 161.99 & 374.01 & 768x8 \\
    Eye State Classification & .9536 & .9549 & 312.57 & 696.51 & 14980x15\\ 
    \bottomrule
  \end{tabular}
\end{table}
\section{Discussion}

>>>>

\author{%
  Eric Su Zhang$^1$ \\
  St. Mark's School of Texas\\
  10600 Preston Rd, Dallas, TX 75230\\
  \texttt{ericspring08@gmail.com} \\
  % examples of more authors
  \And
  Benjamin Standefer$^2$ \\
  St. Mark's School of Texas \\
  10600 Preston Rd, Dallas, TX 75230 \\
  \texttt{bjmstandefer@gmail.com} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

\begin{abstract}
  Automated Machine Learning or AutoML has emerged as a popular field of research. We performed a literature review of existing AutoML papers and conducted a survey on six popluar AutoML frameworks. Many of these frameworks optimize a form of model selection, however, they all require every model to be run and evaluated. We propose a novel framework, SMEML (Smart Model Elimination Machine Learning), that automatically eliminates models that are unlikely to be performant so unnecessary time is not spent training these models. SMEML demonstrates the ability to generate a model with near equal accuracy to a "dumb" model that runs every model on every dataset, but in a fraction of the time.
\end{abstract}

@@

\begin {figure}
\centering
\includegraphics[width=\textwidth]{smeml-flowchart.png}
\caption{SMEML Process}
\end{figure}

\section{Experiments}
\subsection{Experiment Design}
To evaluate our framework, we choose 5 different datasets of diverse size. We ran SMEML on each dataset for 20 iterations of tuning. We compared this against a "dumb" mode which simply runs every model on the dataset. We used the accuracy and time to train as our metrics.

@@

\subsection{Results}
\begin{table}
  \caption{Experiment Results}
  \label{model-options-table}
  \centering
  \begin{tabular}{llllll}
    \toprule
    % group 2, 3 as multicolumn and 4, 5 as multicolumn
    Dataset & \multicolumn{2}{c}{Accuracy} & \multicolumn{2}{c}{Time to Train (sec)} & Size (RxC)\\
    \cmidrule(lr){2-3} \cmidrule(lr){4-5}
    & SMEML & Dumb & SMEML & Dumb \\
    \midrule
    Lung Cancer Prediction & .9839 & .9839 & 143.07 & 317.04 & 309x16\\
    Chronic Kidney Disease Dataset & 1.0 & 1.0 & 419.64 & 788.46 & 400x26\\
    Pima Indians Diabetes Dataset & .7857 & .8052 & 161.99 & 374.01 & 768x8 \\
    Brain Stroke Prediction Dataset & .9458 & .9458 & 114.16 & 370.95 & 4892x11\\
    Stroke Prediction Dataset & .9393 & .9393 & 172.67 & 385.23 & 5110x12 \\
    Eye State Classification & .9536 & .9549 & 312.57 & 696.51 & 14980x15\\ 
    \bottomrule
  \end{tabular}
\end{table}
\section{Discussion}
